LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment

### 2024-06-12 article/main.tex
Prepare article for review

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{balance}
\usepackage{booktabs}
\usepackage[justification=centering]{caption}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{inconsolata}
\usepackage[utf8]{inputenc}
\usepackage{interval}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{url}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{xstring}

\title{LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment}
\author{Andrei Olar\\
Universitatea Babeș-Bolyai, Cluj-Napoca, România\\
\texttt{andrei.olar@ubbcluj.ro}\\}

@@

The next step is to devise HLF prompts derived from both baseline prompts.
The HLF prompts contain additional instructions to generate text that would
comply with certain HLF values.
These HLF values are obtained by computing the statistics outlined above on
the entirety of the target benchmark dataset.
The HLF prompts are constructed from templates that take into account the HLF
values.
The prompt templates are available in the code repository that accompanies this
experiment~\cite{olar2024experimentcode}.
The instructions concerning all choseon HLFs are given concomitently within the
same prompt.
In a similar manner to how we generated the baselines, we run ten trials for
each case (with or without example articles from the target benchmark dataset).

@@

We provide two input texts that are external to our corpuses, one input text per
corpus.
They can be examined online in the
\texttt{\href{https://github.com/koosie0507/llm-tst-consistency/tree/main/data}{data}}
folder of the experiment's Git repository~\cite{olar2024experimentcode}.
These user prompts are used when we're not using an input text from the
corpus itself.

@@

We use Jinja templates to compile the text generation instructions for the LLM.
Both the model prompts and the HLF instructions are constructed using these
templates.
The Jinja templates are available in the
\texttt{\href{https://github.com/koosie0507/llm-tst-consistency/tree/main/data}{templates}}
folder of the experiment's Git repository~\cite{olar2024experimentcode}.

@@

The result tables show $Diff_A$ and $Diff_N$ for each LLM in the context of a
prompt and a dataset.
All result tables for each dataset and prompt variant are available online, in
the experiment's Git repository~\cite{olar2024experimentcode}.

@@

>>>>

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{balance}
\usepackage{booktabs}
\usepackage[justification=centering]{caption}
\usepackage{cleveref}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{inconsolata}
\usepackage[utf8]{inputenc}
\usepackage{interval}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{url}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{xstring}

\usepackage[true]{anonymous-acm}

\title{LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment}
\authoranon{
\author{Andrei Olar\\
Universitatea Babeș-Bolyai, Cluj-Napoca, România\\
\texttt{andrei.olar@ubbcluj.ro}\\}
}

@@

The next step is to devise HLF prompts derived from both baseline prompts.
The HLF prompts contain additional instructions to generate text that would
comply with certain HLF values.
These HLF values are obtained by computing the statistics outlined above on
the entirety of the target benchmark dataset.
The HLF prompts are constructed from templates that take into account the HLF
values.
The prompt templates part of the experiment's source code.
The instructions concerning all choseon HLFs are given concomitently within the
same prompt.
In a similar manner to how we generated the baselines, we run ten trials for
each case (with or without example articles from the target benchmark dataset).

@@

We provide two input texts that are external to our corpuses, one input text per
corpus.
The input texts are located in the
\texttt{\textlinkanon{https://github.com/koosie0507/llm-tst-consistency/tree/main/data}{data}}
folder of the experiment's source code.
These user prompts are used when we're not using an input text from the
corpus itself.

@@

We use Jinja templates to compile the text generation instructions for the LLM.
Both the model prompts and the HLF instructions are constructed using these
templates.
The Jinja templates are located in the
\texttt{\textlinkanon{https://github.com/koosie0507/llm-tst-consistency/tree/main/data}{templates}}
folder of the experiment's source code.

@@

The result tables show $Diff_A$ and $Diff_N$ for each LLM in the context of a
prompt and a dataset.
All result tables for each dataset and prompt variant are available in the
appendix.

@@

\appendix

\section{Additional Result Tables}\label{sec:yelp-tables}
\subsection{Yelp}
\Cref{table-prompt-1-yelp,table-prompt-2-yelp,table-prompt-2-ifd-yelp} show the
experiment results on the corpus of reviews extracted from the Yelp dataset.

\begin{table*}[ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                   & t\_sent                    & n\_uverb                 & n\_uadj                  & simp\_ttr & a\_verb\_pw             & corr\_adj\_var          & corr\_verb\_var         & fkgl                       & a\_kup\_pw               \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\textit{-281.9}}  & \textbf{\textit{-13.22}}   & \textbf{\textit{-25.79}} & -14.56                   & -0.06     & 0.0                     & -1.27                   & -1.14                   & \textbf{\underline{6.89}}  & \textbf{\underline{1.0}} \\ \midrule
            claude3 $Diff\_A$     & \textbf{\textit{-774.0}}  & \textbf{\textit{-27.76}}   & \textbf{\textit{-70.0}}  & -38.0                    & -0.19     & 0.02                    & -3.25                   & -3.39                   & \textbf{\underline{21.68}} & \textbf{\underline{2.9}} \\ \midrule
            gemini $Diff\_N$      & -109.27                   & 0.05                       & -7.25                    & -13.18                   & -0.14     & 0.01                    & -1.01                   & -0.4                    & 1.62                       & -0.4                     \\ \midrule
            gemini $Diff\_A$      & -252.82                   & -0.78                      & -17.5                    & -23.14                   & -0.52     & 0.01                    & -1.85                   & -1.07                   & 7.14                       & -0.93                    \\ \midrule
            gpt $Diff\_N$         & -21.62                    & 2.42                       & -3.8                     & -8.84                    & 0.0       & -0.01                   & -0.8                    & -0.53                   & 8.94                       & -0.37                    \\ \midrule
            gpt $Diff\_A$         & -34.72                    & 9.68                       & -10.54                   & -24.57                   & -0.03     & -0.02                   & -2.37                   & -1.58                   & 19.26                      & -1.03                    \\ \midrule
            command\_r $Diff\_N$  & -40.1                     & 1.22                       & 2.43                     & \textbf{\textit{-13.64}} & 0.05      & \textbf{\textit{-0.04}} & \textbf{\textit{-1.17}} & 0.59                    & \textbf{\textit{-7.25}}    & \textbf{\textit{-1.67}}  \\ \midrule
            command\_r $Diff\_A$  & -75.5                     & 1.5                        & 12.94                    & \textbf{\textit{-34.0}}  & 0.19      & \textbf{\textit{-0.12}} & \textbf{\textit{-2.76}} & 2.83                    & \textbf{\textit{-20.49}}   & \textbf{\textit{-4.76}}  \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\textit{-210.45}} & \textbf{\underline{6.87}}  & \textbf{\textit{-13.46}} & \textbf{\textit{-15.17}} & -0.16     & \textbf{\textit{-0.02}} & \textbf{\textit{-1.78}} & \textbf{\textit{-1.31}} & 3.7                        & \textbf{\textit{-1.58}}  \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\textit{-607.52}} & \textbf{\underline{19.42}} & \textbf{\textit{-41.22}} & \textbf{\textit{-44.77}} & -0.42     & \textbf{\textit{-0.05}} & \textbf{\textit{-5.48}} & \textbf{\textit{-4.34}} & 9.79                       & \textbf{\textit{-4.98}}  \\ \bottomrule
        \end{tabular}%
    }
    \caption{Yelp Results - Prompt Without Examples}
    \label{table-prompt-1-yelp}
\end{table*}

\begin{table*}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word & t\_sent & n\_uverb & n\_uadj & simp\_ttr & a\_verb\_pw & corr\_adj\_var            & corr\_verb\_var & fkgl                       & a\_kup\_pw \\
            \toprule
            claude3 $Diff\_N$     & -121.77 & -4.61   & -9.9     & 18.41   & -0.11     & 0.03        & \textbf{\underline{1.4}}  & -0.33           & 1.81                       & 0.95       \\ \midrule
            claude3 $Diff\_A$     & -394.5  & -11.5   & -37.5    & 60.0    & -0.37     & 0.09        & \textbf{\underline{4.66}} & -1.49           & 5.38                       & 2.62       \\ \midrule
            gemini $Diff\_N$      & -23.49  & 1.52    & -0.55    & -1.29   & -0.02     & -0.01       & 0.09                      & -0.05           & \textbf{\underline{6.41}}  & 0.2        \\ \midrule
            gemini $Diff\_A$      & -83.0   & 3.0     & -2.5     & -6.36   & -0.0      & -0.03       & 0.26                      & -0.08           & \textbf{\underline{19.63}} & 0.53       \\ \midrule
            gpt $Diff\_N$         & 13.66   & 2.83    & -3.65    & -3.19   & 0.04      & -0.04       & -0.24                     & -0.22           & 7.5                        & 0.0        \\ \midrule
            gpt $Diff\_A$         & 55.5    & 9.5     & -9.86    & -12.86  & 0.14      & -0.11       & -0.84                     & -0.22           & 18.67                      & -0.38      \\ \midrule
            command\_r $Diff\_N$  & -188.71 & 0.69    & -10.73   & 1.17    & -0.23     & -0.01       & \textbf{\underline{0.74}} & -0.83           & \textbf{\textit{-5.02}}    & -0.08      \\ \midrule
            command\_r $Diff\_A$  & -516.82 & 2.02    & -29.22   & 8.28    & -0.66     & -0.0        & \textbf{\underline{2.98}} & -2.48           & \textbf{\textit{-14.52}}   & -0.48      \\ \midrule
            llama3\_70b $Diff\_N$ & -202.95 & -7.84   & -13.73   & 1.43    & -0.15     & -0.04       & 0.38                      & -1.39           & 10.67                      & 1.37       \\ \midrule
            llama3\_70b $Diff\_A$ & -561.24 & -18.78  & -49.94   & 5.07    & -0.38     & -0.14       & 1.62                      & -4.81           & 29.26                      & 3.11       \\ \bottomrule
        \end{tabular}%
    }
    \caption{Yelp Results - Prompt With Examples\\Input External To Corpus}
    \label{table-prompt-2-yelp}
\end{table*}
\begin{table*}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                   & t\_sent                 & n\_uverb                  & n\_uadj                  & simp\_ttr               & a\_verb\_pw & corr\_adj\_var          & corr\_verb\_var         & fkgl                    & a\_kup\_pw              \\
            \toprule
            claude3 $Diff\_N$     & -148.13                   & -1.63                   & -3.93                     & \textbf{\textit{-46.03}} & -0.11                   & -0.0        & \textbf{\textit{-3.08}} & -0.31                   & -4.3                    & \textbf{\textit{-1.53}} \\ \midrule
            claude3 $Diff\_A$     & -526.14                   & -7.98                   & -23.86                    & \textbf{\textit{-133.5}} & -0.41                   & -0.0        & \textbf{\textit{-8.98}} & -1.75                   & -21.03                  & \textbf{\textit{-5.34}} \\ \midrule
            gemini $Diff\_N$      & 74.27                     & 0.65                    & 4.67                      & 2.98                     & 0.04                    & -0.0        & -0.22                   & 1.05                    & 1.44                    & -0.65                   \\ \midrule
            gemini $Diff\_A$      & 221.0                     & 2.0                     & 10.5                      & 7.44                     & 0.12                    & -0.03       & -0.85                   & 2.73                    & 3.28                    & -1.79                   \\ \midrule
            gpt $Diff\_N$         & 0.65                      & 4.03                    & -1.19                     & -2.66                    & -0.03                   & -0.01       & -0.17                   & -0.13                   & 1.05                    & -0.67                   \\ \midrule
            gpt $Diff\_A$         & 17.0                      & 11.68                   & -3.68                     & -7.0                     & -0.1                    & -0.04       & -0.43                   & -0.05                   & 0.57                    & -1.75                   \\ \midrule
            command\_r $Diff\_N$  & \textbf{\textit{-236.11}} & \textbf{\textit{-3.6}}  & \textbf{\textit{-0.97}}   & \textbf{\textit{-27.04}} & \textbf{\textit{-0.23}} & 0.0         & -1.24                   & \textbf{\textit{-1.08}} & \textbf{\textit{-2.13}} & \textbf{\textit{-1.09}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\textit{-727.0}}  & \textbf{\textit{-9.24}} & \textbf{\underline{0.76}} & \textbf{\textit{-68.5}}  & \textbf{\textit{-0.64}} & 0.02        & -2.89                   & \textbf{\textit{-3.08}} & \textbf{\textit{-5.5}}  & \textbf{\textit{-3.0}}  \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\textit{-333.03}} & \textbf{\textit{-5.19}} & 4.43                      & \textbf{\textit{-21.38}} & -0.16                   & -0.03       & \textbf{\textit{-1.77}} & -0.03                   & 1.87                    & -0.44                   \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\textit{-687.34}} & \textbf{\textit{-3.42}} & 10.7                      & \textbf{\textit{-61.64}} & -0.31                   & -0.04       & \textbf{\textit{-5.6}}  & -0.89                   & 3.0                     & -1.92                   \\ \bottomrule
        \end{tabular}%
    }
    \caption{Yelp Results - Prompt With Examples\\Input From Corpus}
    \label{table-prompt-2-ifd-yelp}
\end{table*}

\section{Additional Plots}

\subsection{GPT}

\Cref{fig:gpt-prompt1-cnn,fig:gpt-prompt1-yelp,fig:gpt-prompt2-cnn,fig:gpt-prompt2-yelp,fig:gpt-prompt2-cnn-ifd,fig:gpt-prompt2-yelp-ifd}
show the experiment results for the Claude 3 Opus large language model.

\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail.png}
    \caption{GPT on CNN Corpus\\Prompt Without Examples}
    \label{fig:gpt-prompt1-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-gpt-yelp/prompt_1-gpt-yelp.png}
    \caption{GPT on Yelp Corpus\\Prompt Without Examples}
    \label{fig:gpt-prompt1-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail.png}
    \caption{GPT on CNN Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:gpt-prompt2-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-gpt-yelp/prompt_2-gpt-yelp.png}
    \caption{GPT on Yelp Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:gpt-prompt2-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail.png}
    \caption{GPT on CNN Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:gpt-prompt2-cnn-ifd}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-gpt-yelp/prompt_2-gpt-yelp.png}
    \caption{GPT on Yelp Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:gpt-prompt2-yelp-ifd}
\end{figure*}

\subsection{Gemini}

\Cref{fig:gemini-prompt1-cnn,fig:gemini-prompt1-yelp,fig:gemini-prompt2-cnn,fig:gemini-prompt2-yelp,fig:gemini-prompt2-cnn-ifd,fig:gemini-prompt2-yelp-ifd}
show the experiment results for the Claude 3 Opus large language model.

\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-gemini-cnn_dailymail/prompt_1-gemini-cnn_dailymail.png}
    \caption{Gemini on CNN Corpus\\Prompt Without Examples}
    \label{fig:gemini-prompt1-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-gemini-yelp/prompt_1-gemini-yelp.png}
    \caption{Gemini on Yelp Corpus\\Prompt Without Examples}
    \label{fig:gemini-prompt1-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail.png}
    \caption{Gemini on CNN Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:gemini-prompt2-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-gemini-yelp/prompt_2-gemini-yelp.png}
    \caption{Gemini on Yelp Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:gemini-prompt2-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail.png}
    \caption{Gemini on CNN Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:gemini-prompt2-cnn-ifd}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-gemini-yelp/prompt_2-gemini-yelp.png}
    \caption{Gemini on Yelp Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:gemini-prompt2-yelp-ifd}
\end{figure*}

\subsection{Claude3}

\Cref{fig:claude3-prompt1-cnn,fig:claude3-prompt1-yelp,fig:claude3-prompt2-cnn,fig:claude3-prompt2-yelp,fig:claude3-prompt2-cnn-ifd,fig:claude3-prompt2-yelp-ifd}
show the experiment results for the Claude 3 Opus large language model.

\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail.png}
    \caption{Claude3 on CNN Corpus\\Prompt Without Examples}
    \label{fig:claude3-prompt1-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-claude3-yelp/prompt_1-claude3-yelp.png}
    \caption{Claude3 on Yelp Corpus\\Prompt Without Examples}
    \label{fig:claude3-prompt1-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-claude3-cnn_dailymail/prompt_2-claude3-cnn_dailymail.png}
    \caption{Claude3 on CNN Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:claude3-prompt2-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-claude3-yelp/prompt_2-claude3-yelp.png}
    \caption{Claude3 on Yelp Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:claude3-prompt2-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-claude3-cnn_dailymail/prompt_2-claude3-cnn_dailymail.png}
    \caption{Claude3 on CNN Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:claude3-prompt2-cnn-ifd}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-claude3-yelp/prompt_2-claude3-yelp.png}
    \caption{Claude3 on Yelp Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:claude3-prompt2-yelp-ifd}
\end{figure*}

\subsection{Llama3}

\Cref{fig:llama3_70b-prompt1-cnn,fig:llama3_70b-prompt1-yelp,fig:llama3_70b-prompt2-cnn,fig:llama3_70b-prompt2-yelp,fig:llama3_70b-prompt2-cnn-ifd,fig:llama3_70b-prompt2-yelp-ifd}
show the experiment results for the Claude 3 Opus large language model.

\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-llama3_70b-cnn_dailymail/prompt_1-llama3_70b-cnn_dailymail.png}
    \caption{Llama3 on CNN Corpus\\Prompt Without Examples}
    \label{fig:llama3_70b-prompt1-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-llama3_70b-yelp/prompt_1-llama3_70b-yelp.png}
    \caption{Llama3 on Yelp Corpus\\Prompt Without Examples}
    \label{fig:llama3_70b-prompt1-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-llama3_70b-cnn_dailymail/prompt_2-llama3_70b-cnn_dailymail.png}
    \caption{Llama3 on CNN Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:llama3_70b-prompt2-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-llama3_70b-yelp/prompt_2-llama3_70b-yelp.png}
    \caption{Llama3 on Yelp Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:llama3_70b-prompt2-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-llama3_70b-cnn_dailymail/prompt_2-llama3_70b-cnn_dailymail.png}
    \caption{Llama3 on CNN Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:llama3_70b-prompt2-cnn-ifd}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-llama3_70b-yelp/prompt_2-llama3_70b-yelp.png}
    \caption{Llama3 on Yelp Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:llama3_70b-prompt2-yelp-ifd}
\end{figure*}

\subsection{Command R+}

\Cref{fig:command_r-prompt1-cnn,fig:command_r-prompt1-yelp,fig:command_r-prompt2-cnn,fig:command_r-prompt2-yelp,fig:command_r-prompt2-cnn-ifd,fig:command_r-prompt2-yelp-ifd}
show the experiment results for the Claude 3 Opus large language model.

\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail.png}
    \caption{Command R on CNN Corpus\\Prompt Without Examples}
    \label{fig:command_r-prompt1-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_1/prompt_1-command_r-yelp/prompt_1-command_r-yelp.png}
    \caption{Command R on Yelp Corpus\\Prompt Without Examples}
    \label{fig:command_r-prompt1-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail.png}
    \caption{Command R on CNN Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:command_r-prompt2-cnn}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2/prompt_2-command_r-yelp/prompt_2-command_r-yelp.png}
    \caption{Command R on Yelp Corpus\\Prompt With Examples\\Extraneous Input}
    \label{fig:command_r-prompt2-yelp}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail.png}
    \caption{Command R on CNN Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:command_r-prompt2-cnn-ifd}
\end{figure*}
\begin{figure*}[ht]
    \includegraphics[width=\textwidth,height=0.9\textheight,scale=1]{plots/prompt_2_ifd/prompt_2-command_r-yelp/prompt_2-command_r-yelp.png}
    \caption{Command R on Yelp Corpus\\Prompt With Examples\\Input from Corpus}
    \label{fig:command_r-prompt2-yelp-ifd}
\end{figure*}
